$\epsilon$-explicit analysis of DPG

### 2012-04-05 docs/NewBCRobustness_paper/paper.tex
fixed typo
git-svn-id: https://svn.ices.utexas.edu/repos/camellia@448 36274a68-8941-4c93-80ef-affaed5139da

\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{Robust DPG II}
\date{}
\begin{document}

@@

The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.  
%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.

Instead, the goal of this paper will to be derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.  We seek to derive an estimate
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are characterized using
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i} \coloneqq C_1^i\|u\| + C_2^i\|\sigma\| + C_3^i\|\widehat{u}\| + C_4^i\|\widehat{f}_n\|,\quad i = 1,2
\]
%As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.  \textcolor{red}{Not sure if I need this sentence here.}
To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
\]
Our goal is to explicitly derive the constants $C^1_1,\ldots C^1_4$ and $C^2_1,\ldots C^2_4$ that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependence of such $C^i_j$ on $\epsilon$.  Our strategy for doing so is broken down into three parts.

>>>>

\author{Tan Bui-Thanh \and Jesse Chan \and Leszek Demkowicz \and Norbert Heuer}
\title{$\epsilon$-explicit analysis of DPG}
\date{}
\begin{document}

@@

%The first condition is satisfied by first decoupling norms on $\left(\tau,v\right)$ such that
%\[
%\left\|\left(\tau,v\right)\right\|_V = \|\tau\|_{H({\rm div},\Omega_h)} +  \|v\|_{H^1(\Omega_h)}.
%\]
%where $\|\tau\|_{H({\rm div},\Omega_h)}$ and $ \|v\|_{H^1(\Omega_h)}$ are both constructed as the sum of norm and seminorms on each respective space.  Ensuring that each seminorm/normed term is of the same order will allow for smooth solutions (under some assumptions on $\beta$).  
The main goal of this paper is to derive a test norm that \textit{does not induce boundary layers in the optimal test functions}, but still induces an energy norm performs well for $\epsilon \ll 1$.  The avoidance of boundary layers in the test norm will be described in more detail in the section detailing numerical experiments.  Towards the goal of a well-performing energy norm, we will seek to derive $\epsilon$-explicit bounds on the finite element error by the best approximation error, and to characterize the dependence of such bounds upon the test norm.  We seek to derive an estimate
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}
\]
where both $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ are characterized using
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,i} \coloneqq C_1^i\|u\| + C_2^i\|\sigma\| + C_3^i\|\widehat{u}\| + C_4^i\|\widehat{f}_n\|,\quad i = 1,2
\]
%As it may not be possible to derive $O(1)$ constants for each $C_j^i$, we will aim instead for a quasi-robust estimate, where some constants are allowed to depend on $\epsilon$.  \textcolor{red}{Not sure if I need this sentence here.}
To derive the above $\epsilon$-explicit bounds on the finite element error in norm $U,1$ by the best approximation error in norm $U,2$, we need to show that the DPG energy norm (in which our finite element solution is optimal), is bounded from above and below 
\[
\left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,1} \lesssim  \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_E \lesssim \left\| \left(u,\sigma,\widehat{u},\widehat{f}_n\right)\right \|_{U,2}.
\]
Our goal is to explicitly derive the constants $C^1_1,\ldots C^1_4$ and $C^2_1,\ldots C^2_4$ that define the norms $\|\cdot\|_{U,1}$ and $\|\cdot\|_{U,2}$ respectively, taking into account any dependence of such $C^i_j$ on $\epsilon$.  Our strategy for doing so is broken down into three parts.
